Preprocessing

### 2024-04-05 analysis/preprocessing.Rmd
Update preprocessing.Rmd

```{r}
d_journals <- d_journals %>%
  mutate(sample_id = factor(sample_id),
         journal_name = factor(journal),
         is_empirical = as.logical(fct_recode(journal_empirical, T = "Yes", F = "No")),
         has_ppc = fct_recode(anyPPC, 
                             "ARCHIVE" = "ARCHIVE ONLY", 
                             "NO IMPLICIT" = "NO (there are no PPC options)",
                             "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized, cope, field = field_harmonized, jif)
```
#Reclassify PPC name in JOURNAL OF CLINICAL PSYCHIATRY due to quotation marks in raw data name impeding inclusion above

>>>>

```{r}
d_journals <- d_journals %>%
  mutate(sample_id = factor(sample_id),
         journal_name = factor(journal),
         is_empirical = as.logical(fct_recode(journal_empirical, T = "Yes", F = "No")),
         has_ppc = fct_recode(anyPPC, 
                             "NO IMPLICIT" = "NO (there are no PPC options)",
                             "NO EXPLICIT" = "NO (explicit statement that PPC is not accepted)")) %>%
  select(sample_id, journal_name, is_empirical, has_ppc, ppc_type = PPC_type, ppc_name = name_harmonized, ppc_description = description, ppc_length = length_harmonized, ppc_time = time_harmonized, ppc_ref = ref_harmonized, ppc_review = review_harmonized, cope, field = field_harmonized, jif)
```
#Reclassify PPC name in JOURNAL OF CLINICAL PSYCHIATRY due to quotation marks in raw data name impeding inclusion above
